sem

### 2023-02-14 scripts/workshop/sem.Rmd
latent variable modeling attempt

```{r}
potential <- comm_data %>% mutate(log_cc = log10(cc), log_size = log10(size)) %>% select(cc, log_cc, size, log_size, MeanWaterTempPredC, Prevalence) %>% drop_na() %>% filter(MeanWaterTempPredC > 0)
cor(potential[,c(2,4,5)])
```

```{r}
potential_formula <- "potential =~ log_cc + log_size + MeanWaterTempPredC"
potential_model <- sem(potential_formula, potential)
```

@@

```{r}
potential_formula_1 <- "
potential =~ log_cc + log_size + MeanWaterTempPredC

Prevalence ~ potential
"

>>>>

First step is to measure reliability. There should be a sufficient amount of reliability (at least >0.5 but >0.8 or >0.9 is better)
```{r}
potential <- comm_data %>% mutate(log_cc = log10(cc), log_size = log10(size), inv_temp = MeanWaterTempPredC*-1) %>% select(cc, log_cc, size, log_size, MeanWaterTempPredC, inv_temp, Prevalence) %>% drop_na() %>% filter(MeanWaterTempPredC > 0)
indicators <- potential %>% select(log_cc, log_size, inv_temp)
cor(indicators)

#find average correlation among all variables

r <- mean(c((cor(indicators)[2,1]), (cor(indicators)[3,1]), (cor(indicators)[3,2])))
sqrt(r)
```

```{r}
potential_formula <- "potential =~ log_cc + log_size + inv_temp"
potential_model <- sem(potential_formula, potential)
```

@@

```{r}
print(modindices(potential_model, na.remove=F))
```

```{r}
potential_formula_1 <- "
potential =~ log_cc + log_size + inv_temp 
Prevalence ~ potential
"
